---

title: "Percona Server for MongoDB: Storage Engine comparison"
author: "Percona Lab"
generated on:`r format(Sys.Date(), "%B %d, %Y")`
output:
  md_document:
    variant: markdown_github

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(knitr)
library(plyr)

label_custom <- function(variable, value) {
    if (variable=="size") {
        return (paste(variable,":",value))
    } else if (variable=="engine"){
        return (as.character(value))
    } else {
        return (value)
    }
}

data <- read.csv("../alldata.csv", header=T)
data_ft <- subset(data, engine == "ft")
data_wt <- subset(data, engine == "wt")
data_rocks <- subset(data, engine == "rocks")

nothreads <- c(1,2,4,8,16,24,32,40,48,64,128,256,512)

```
# Percona Server for MongoDB 3.0.8-1.2 - data set that fits in RAM 

## Setup

* Client (sysbench) and server are on the same machine
* CPU: 48 logical CPU threads servers Intel(R) Xeon(R) CPU E5-2680 v3 @ 2.50GHz
* sysbench with mongodb support, 16 collections x 2M documents, uniform distribution. 


## Throughput per threads and workload, summary for each engine

```{r engines,  fig.width=16, warning=FALSE, echo=FALSE}
print(ggplot(data_ft, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter() + scale_colour_discrete(name = "") + facet_grid(. ~ user_provided_threads) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle("Percona Server for MongoDB / throughput per threads (PerconaFT)") + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,data_ft$tps)))  + scale_x_discrete(breaks = c(600)) + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24)))

print(ggplot(data_wt, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter() + scale_colour_discrete(name = "") + facet_grid(. ~ user_provided_threads) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle("Percona Server for MongoDB / throughput per threads (WiredTiger)") + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,data_wt$tps)))  + scale_x_discrete(breaks = c(600)) + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24)))

print(ggplot(data_rocks, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter() + scale_colour_discrete(name = "") + facet_grid(. ~ user_provided_threads) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle("Percona Server for MongoDB / throughput per threads (RocksDB)") + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,data_rocks$tps)))  + scale_x_discrete(breaks = c(600)) + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24)))


```

## Throughput per threads and workload, details. 

```{r ft,  fig.width=16, warning=FALSE, echo=FALSE}

for (t in nothreads) {
    subdata <- subset(data_ft, threads == t)
	gtitle <- paste("Percona Server for MongoDB / throughput (PerconaFT/", t," threads)")
	print(ggplot(subdata, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter() + scale_colour_discrete(name = "") + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle(gtitle) + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,subdata$tps)))  + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24)))
}
```

## Throughput per threads and workload, WiredTiger

```{r wt,  fig.width=16, warning=FALSE, echo=FALSE}


for (t in nothreads) {
    subdata <- subset(data_wt, threads == t)
	gtitle <- paste("Percona Server for MongoDB / throughput (WiredTiger/", t," threads)")
	print(ggplot(subdata, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter() + scale_colour_discrete(name = "") + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle(gtitle) + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,subdata$tps)))  + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24)))
}
```

## Throughput per threads and workload, RocksDB

```{r rocks,  fig.width=16, warning=FALSE, echo=FALSE}


for (t in nothreads) {
    subdata <- subset(data_rocks, threads == t)
	gtitle <- paste("Percona Server for MongoDB / throughput (RocksDB/", t," threads)")
	print(ggplot(subdata, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter() + scale_colour_discrete(name = "") + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle(gtitle) + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,subdata$tps)))  + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24)))
}
```
