---

title: "Percona Server for MongoDB: CPU and I/O scalability for
WiredTiger and RocksDB"
author: "Percona Lab"
generated on:`r format(Sys.Date(), "%B %d, %Y")`
output:
  md_document:
    variant: markdown_github

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(knitr)
library(plyr)

label_custom <- function(variable, value) {
    if (variable=="version") {
       return(sub("upstream","M",sub("psmdb","P",value)))
    } else if (variable=="range_size" | variable=="Group.4") {
		return(paste("rs: ",value/1000,"k"))
    }else {
      return (as.character(value))
    }
}

threadScalability <- read.csv("../thread_scalability.csv", header=T)
memScalability <- read.csv("../memory_scalability.csv", header=T)

nothreads <- c(1,3,5,8,13,20,31,46,68,100,145,210,300,430,630,870,1000,1200)
memorySizes <- c(20,30,40,50,60,70,80,90,100,110,120,130,140,150,160,170,180,190,200,210)
filesystems <- c("ext4","xfs")
configurations <- c("rocks0","wt0","wt1","wt2")

```
# Percona Server for MongoDB 3.2.4-1.rc2 - CPU and I/O scalability 

## Setup

* Setup information pending 

## Configuration reference

### rocks0

storage.rocksdb.configString:
"bytes_per_sync=16m;max_background_flushes=3;max_background_compactions=12;max_write_buffer_number=4;max_bytes_for_level_base=1500m;target_file_size_base=200m;level0_slowdown_writes_trigger=12;write_buffer_size=400m;compression_per_level=kSnappyCompression:kSnappyCompression:kSnappyCompression:kSnappyCompression:kSnappyCompression:kSnappyCompression:kSnappyCompression;optimize_filters_for_hits=true"

### wt0

--syncdelay=900 --wiredTigerJournalCompressor=none --wiredTigerCacheSizeGB=$cache_size

### wt1

--syncdelay=900 --wiredTigerJournalCompressor=zlib --wiredTigerCacheSizeGB=$cache_size

### wt2

--syncdelay=900 --wiredTigerJournalCompressor=snappy --wiredTigerCacheSizeGB=$cache_size

## CPU Scalability tests 

```{r cpu, fig.width=36, fig.height=16, warning=FALSE, echo=FALSE}

for (dist in c("uniform","pareto")) {
    for (wl in c("oltp","oltp_ro")) { 
        data <- subset(threadScalability, distribution == dist & test == wl)
        p <- ggplot(data, aes(x=ts, y=tps, color=as.factor(engine))) +
            facet_grid(configuration ~ user_provided_threads) +
            geom_jitter(size=8,width=0.2,height=0.2) +
            theme_bw() +
            labs(x="time (secs)",y="throughput (tps)",title=paste("Throughput per
            engine, configuration and threads (", dist, ",", wl, ")")) + expand_limits(x=0,y=0) +
            scale_y_continuous(breaks=extended_range_breaks()(rbind(0,data$tps))) +
            scale_x_continuous(breaks=c(maxtime)) + 
            theme(panel.grid = element_line(colour="#010101",size=1),
            panel.background = element_rect(colour="#000000"),
            plot.background = element_rect(colour="#000000"),
            strip.background = element_rect(colour="#010101"),
            text=element_text(size=50),
            strip.text=element_text(size=60))
        print(p)
    }
}

```

## Memory Scalability tests

The memory scalability tests were all done using 100 client threads.
All graphs faceted by memory and configuration. 

```{r mem, fig.width=36, fig.height=16, warning=FALSE, echo=FALSE}
for (dist in c("uniform","pareto")) {
    for (wl in c("oltp","oltp_ro")) { 
        for (fs in filesystems) {
            data <- subset(memScalability, distribution == dist & test == wl & filesystem == fs)
            p <- ggplot(data, aes(x=ts, y=tps, color=as.factor(engine))) +
                facet_grid(configuration ~ memory) +
                geom_jitter(size=8,width=0.2,height=0.2) +
                theme_bw() +
                labs(x="time (secs)",y="throughput (tps)",title=paste("Throughput per
                engine, configuration and threads (", dist, ",", wl, ",", fs, ")")) + expand_limits(x=0,y=0) +
                scale_y_continuous(breaks=extended_range_breaks()(rbind(0,data$tps))) +
                scale_x_continuous(breaks=c(maxtime)) + 
                theme(panel.grid = element_line(colour="#010101",size=1),
                panel.background = element_rect(colour="#000000"),
                plot.background = element_rect(colour="#000000"),
                strip.background = element_rect(colour="#010101"),
                text=element_text(size=50),
                strip.text=element_text(size=60))
            print(p)
        }
    }
}
```

## Throughput detail 

### Thread scalability 

```{r tps_ts, fig.width=36, fig.height=16, warning=F, echo=F}
for (dist in c("uniform","pareto")) {
    for (wl in c("oltp","oltp_ro")) {
        for (t in nothreads) {
            data <- subset(threadScalability, distribution == dist & test == wl & user_provided_threads == t)
        p <- ggplot(data, aes(x=ts, y=tps, color=as.factor(engine))) +
            facet_grid(configuration ~ .) +
            geom_jitter(size=8,width=0.2,height=0.2) +
            theme_bw() +
            labs(x="time (secs)",y="throughput (tps)",title=paste("Throughput per
            engine and configuration (", dist, ",", wl, ", ", t, " threads)")) + expand_limits(x=0,y=0) +
            scale_y_continuous(breaks=extended_range_breaks()(rbind(0,data$tps))) +
            theme(panel.grid = element_line(colour="#010101",size=1),
            panel.background = element_rect(colour="#000000"),
            plot.background = element_rect(colour="#000000"),
            strip.background = element_rect(colour="#010101"),
            text=element_text(size=50),
            strip.text=element_text(size=60))
        print(p)
        }
    }
}
```

### Memory scalability

```{r tps_ms, fig.width=36, fig.height=16, warning=FALSE, echo=FALSE}
for (dist in c("uniform","pareto")) {
    for (wl in c("oltp","oltp_ro")) { 
        for (fs in filesystems) {
            for (m in memorySizes) {
                data <- subset(memScalability, distribution == dist & test == wl & filesystem == fs & memory == m)
                p <- ggplot(data, aes(x=ts, y=tps, color=as.factor(engine))) +
                    facet_grid(configuration ~ .) +
                    geom_jitter(size=8,width=0.2,height=0.2) +
                    theme_bw() +
                    labs(x="time (secs)",y="throughput (tps)",title=paste("Throughput per
                    engine and configuration (", dist, ",", wl, ",", fs, ", ", m,"GB)")) + expand_limits(x=0,y=0) +
                    scale_y_continuous(breaks=extended_range_breaks()(rbind(0,data$tps))) +
                    theme(panel.grid = element_line(colour="#010101",size=1),
                    panel.background = element_rect(colour="#000000"),
                    plot.background = element_rect(colour="#000000"),
                    strip.background = element_rect(colour="#010101"),
                    text=element_text(size=50),
                    strip.text=element_text(size=60))
                print(p)
            }
        }
    }
}
```

