---

title: "Percona Server for MongoDB: Storage Engine comparison"
author: "Percona Lab"
generated on:`r format(Sys.Date(), "%B %d, %Y")`
output:
  md_document:
    variant: markdown_github

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(knitr)
library(plyr)

build_label_arr <- function(value, dimension) {
    res <- c()
    for (i in 1:dimension) {
    	res[i] = value
    }
    return (res)
}

label_custom <- function(variable, value) {
	if (variable=="version") {
		if (value=="psmdb3.0") {
			return (build_label_arr("P3.0",length(value)))
		} else if (value=="psmdb3.2") {
		    return (build_label_arr("P3.2",length(value)))
		} else if (value=="upstream3.0") {
		    return (build_label_arr("M3.0",length(value)))
		} else if (value=="upstream3.2") {
		    return (build_label_arr("M3.2",length(value)))
		}
	} else {
		return (as.character(value))
	}
}

data <- read.csv("../alldata-bothversions.csv", header=T)

data_ft <- subset(data, engine == "ft")
data_wt <- subset(data, engine == "wt")
data_rocks <- subset(data, engine == "rocks")
data_stable_tps_oltp <- subset(data, ts>=300 & workload=="oltp")
data_stable_tps_oltp_ro <- subset(data, ts>=300 & workload=="oltp_ro")

aggdata_oltp <- aggregate(data_stable_tps_oltp$tps, by=list(data_stable_tps_oltp$engine_and_version, data_stable_tps_oltp$user_provided_threads), FUN=mean, na.rm=TRUE)
aggdata_oltp_ro <- aggregate(data_stable_tps_oltp_ro$tps, by=list(data_stable_tps_oltp_ro$engine_and_version, data_stable_tps_oltp_ro$user_provided_threads), FUN=mean, na.rm=TRUE)

print(head(aggdata_oltp))

nothreads <- c(1,2,4,8,16,24,32,40,48,64,128,256,512)

```
# Percona Server for MongoDB 3.0.10-1.5 and 3.2.0-1.0 - data set that fits in RAM 

## Setup

* Client (sysbench) and server are on the same machine
* CPU: 48 logical CPU threads servers Intel(R) Xeon(R) CPU E5-2680 v3 @ 2.50GHz
* 128GB RAM (64GB storage engine cache)
* sysbench with mongodb support, 16 collections x 2M documents (~6GB compressed), uniform distribution. 

## Throughput per threads and workload

```{r global, fig.width=16, warning=FALSE, echo=FALSE}

ss=subset(aggdata_oltp)
ss2=subset(aggdata_oltp_ro)

m <- ggplot(ss, aes(x=as.factor(Group.2),y=as.numeric(x),color=as.factor(Group.1),group=Group.1))
m+geom_line()+geom_point(size=1)+labs(x="Threads",y="Throughput,tps",title="sysbench OLTP")+scale_color_tableau(name="Version")+scale_y_continuous(breaks=extended_range_breaks()(rbind(0,data_stable_tps_oltp$tps)),labels = scales::comma)+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24))

m <- ggplot(ss2, aes(x=as.factor(Group.2),y=as.numeric(x),color=as.factor(Group.1),group=Group.1))
m+geom_line()+geom_point(size=1)+labs(x="Threads",y="Throughput,tps",title="sysbench OLTP read only")+scale_color_tableau(name="Version")+scale_y_continuous(breaks=extended_range_breaks()(rbind(0,data_stable_tps_oltp_ro$tps)),labels = scales::comma)+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24))
```

## Throughput per threads and workload, summary for each version and engine

Versions marked with an 'M' correspond to upstream MongoDB, and with a 'P' to Percona Server for MongoDB

```{r engines,  fig.width=16, warning=FALSE, echo=FALSE}

print(ggplot(data_ft, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter() + scale_colour_discrete(name = "") + facet_grid(engine + version~ user_provided_threads, labeller=label_custom) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle("Percona Server for MongoDB / throughput per threads (PerconaFT)") + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,data_ft$tps)))  + scale_x_discrete(breaks = c(600)) + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24)))

print(ggplot(data_wt, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter() + scale_colour_discrete(name = "") + facet_grid(engine + version ~ user_provided_threads, labeller=label_custom) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle("Percona Server for MongoDB / throughput per threads (WiredTiger)") + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,data_wt$tps)))  + scale_x_discrete(breaks = c(600)) + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24)))

print(ggplot(data_rocks, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter() + scale_colour_discrete(name = "") + facet_grid(engine + version ~ user_provided_threads, labeller=label_custom) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle("Percona Server for MongoDB / throughput per threads (RocksDB)") + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,data_rocks$tps)))  + scale_x_discrete(breaks = c(600)) + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24)))


```

## Throughput per threads and workload, details. 

```{r ft,  fig.width=16, warning=FALSE, echo=FALSE}

for (t in nothreads) {
    subdata <- subset(data_ft, threads == t)
	gtitle <- paste("Percona Server for MongoDB / throughput (PerconaFT/", t," threads)")
	print(ggplot(subdata, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter() + scale_colour_discrete(name = "") + facet_grid(. ~ engine_and_version) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle(gtitle) + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,subdata$tps)))  + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24)))
}
```

## Throughput per threads and workload, WiredTiger

```{r wt,  fig.width=16, warning=FALSE, echo=FALSE}


for (t in nothreads) {
    subdata <- subset(data_wt, threads == t)
	gtitle <- paste("Percona Server for MongoDB / throughput (WiredTiger/", t," threads)")
	print(ggplot(subdata, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter() + scale_colour_discrete(name = "") + facet_grid(. ~ engine_and_version) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle(gtitle) + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,subdata$tps)))  + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24)))
}
```

## Throughput per threads and workload, RocksDB

```{r rocks,  fig.width=16, warning=FALSE, echo=FALSE}


for (t in nothreads) {
    subdata <- subset(data_rocks, threads == t)
	gtitle <- paste("Percona Server for MongoDB / throughput (RocksDB/", t," threads)")
	print(ggplot(subdata, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter() + scale_colour_discrete(name = "") + facet_grid(. ~ engine_and_version) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle(gtitle) + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,subdata$tps)))  + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=20), strip.text=element_text(size=24)))
}
```
