---

title: "Percona Server for MongoDB: Storage Engine comparison"
author: "Percona Lab"
generated on:`r format(Sys.Date(), "%B %d, %Y")`
output:
  md_document:
    variant: markdown_github

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(knitr)
library(plyr)

label_custom <- function(variable, value) {
    if (variable=="version") {
       return(sub("upstream","M",sub("psmdb","P",value)))
    } else {
      return (as.character(value))
    }
}

data <- read.csv("../alldata.csv", header=T)

data_uniform <- subset(data, distribution == "uniform" & version == "psmdb-3.2")
data_pareto <- subset(data, distribution == "pareto" & version == "psmdb-3.2")

data_ft <- subset(data, engine == "ft" & version == "psmdb-3.2")
data_wt <- subset(data, engine == "wt" & version == "psmdb-3.2")
data_rocks <- subset(data, engine == "rocks" & version == "psmdb-3.2")

data_stable_oltp_pareto <- subset(data_pareto, ts>=300 & workload=="oltp")
data_stable_oltp_uniform <- subset(data_uniform, ts>=300 & workload=="oltp")
data_stable_oltp_ro_pareto <- subset(data_pareto, ts>=300 & workload=="oltp_ro")
data_stable_oltp_ro_uniform <- subset(data_uniform, ts>=300 & workload=="oltp_ro")

data_oltp_pareto <- subset(data_pareto,  workload=="oltp")
data_oltp_uniform <- subset(data_uniform,  workload=="oltp")
data_oltp_ro_pareto <- subset(data_pareto,  workload=="oltp_ro")
data_oltp_ro_uniform <- subset(data_uniform,  workload=="oltp_ro")

aggdata_oltp_pareto <- aggregate(data_oltp_pareto$tps, by=list(data_oltp_pareto$engine, data_oltp_pareto$user_provided_threads), FUN=function(x) quantile(x, probs = 0.99))
aggdata_oltp_uniform <- aggregate(data_oltp_uniform$tps, by=list(data_oltp_uniform$engine, data_oltp_uniform$user_provided_threads), FUN=function(x) quantile(x, probs = 0.99))
aggdata_oltp_ro_pareto <- aggregate(data_oltp_ro_pareto$tps, by=list(data_oltp_ro_pareto$engine, data_oltp_ro_pareto$user_provided_threads), FUN=function(x) quantile(x, probs = 0.99))
aggdata_oltp_ro_uniform <- aggregate(data_oltp_ro_uniform$tps, by=list(data_oltp_ro_uniform$engine, data_oltp_ro_uniform$user_provided_threads), FUN=function(x) quantile(x, probs = 0.99))

nothreads <- c(1,4,16,32,48,128,512)

```
# Percona Server for MongoDB 3.2.0-1.0 - data that does not fit in RAM 

## Setup

* Client and server on different (equal) machines.
* Client sofwware is sysbench (https://github.com/Percona-Lab/sysbench/tree/dev-mongodb-support).
* CPU: 56 logical CPU threads (Intel(R) Xeon(R) CPU E5-2683 v3 @ 2.00GHz).
* 20GB RAM (limited via cgroup).
* sysbench with mongodb support, 16 collections x 60M documents (~50G uncompressed), uniform and pareto distributions. 

## Throughput per threads and workload

```{r global, fig.width=36, fig.height=16, warning=FALSE, echo=FALSE}

m <- ggplot(aggdata_oltp_pareto, aes(x=as.factor(Group.2),y=as.numeric(aggdata_oltp_pareto$x),color=as.factor(Group.1),group=Group.1))
m+geom_line()+geom_point(size=4) + labs(x="Threads",y="Throughput,tps",title="sysbench OLTP - Pareto")+scale_color_tableau(name="Engine & Version")+scale_y_continuous(breaks=extended_range_breaks()(rbind(0,data_stable_oltp_pareto$tps)),labels = scales::comma)+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60))

m <- ggplot(aggdata_oltp_uniform, aes(x=as.factor(Group.2),y=as.numeric(aggdata_oltp_uniform$x),color=as.factor(Group.1),group=Group.1))
m+geom_line()+geom_point(size=4) + labs(x="Threads",y="Throughput,tps",title="sysbench OLTP - Uniform")+scale_color_tableau(name="Engine & Version")+scale_y_continuous(breaks=extended_range_breaks()(rbind(0,data_stable_oltp_uniform$tps)),labels = scales::comma)+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60))

m <- ggplot(aggdata_oltp_ro_pareto, aes(x=as.factor(Group.2),y=as.numeric(aggdata_oltp_ro_pareto$x),color=as.factor(Group.1),group=Group.1))
m+geom_line()+geom_point(size=4) + labs(x="Threads",y="Throughput,tps",title="sysbench OLTP read only - Pareto")+scale_color_tableau(name="Engine & Version")+scale_y_continuous(breaks=extended_range_breaks()(rbind(0,data_stable_oltp_ro_pareto$tps)),labels = scales::comma)+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60))

m <- ggplot(aggdata_oltp_ro_uniform, aes(x=as.factor(Group.2),y=as.numeric(aggdata_oltp_ro_uniform$x),color=as.factor(Group.1),group=Group.1))
m+geom_line()+geom_point(size=4) + labs(x="Threads",y="Throughput,tps",title="sysbench OLTP read only - Uniform")+scale_color_tableau(name="Engine & Version")+scale_y_continuous(breaks=extended_range_breaks()(rbind(0,data_stable_oltp_ro_uniform$tps)),labels = scales::comma)+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60))
```

## Throughput per threads and workload, summary for engine

```{r engines,  fig.width=36, fig.height=26, warning=FALSE, echo=FALSE}

print(ggplot(data_ft, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter(size=4) + scale_colour_discrete(name = "") + facet_grid( distribution ~ user_provided_threads, labeller=label_custom) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle("Percona Server for MongoDB / throughput per threads (PerconaFT)") + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,data_ft$tps)))  + scale_x_discrete(breaks = c(600)) + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60)))

print(ggplot(data_wt, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter(size=4) + scale_colour_discrete(name = "") + facet_grid(distribution ~ user_provided_threads, labeller=label_custom) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle("Percona Server for MongoDB / throughput per threads (WiredTiger)") + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,data_wt$tps)))  + scale_x_discrete(breaks = c(600)) + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60)))

print(ggplot(data_rocks, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter(size=4) + scale_colour_discrete(name = "") + facet_grid(distribution ~ user_provided_threads, labeller=label_custom) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle("Percona Server for MongoDB / throughput per threads (RocksDB)") + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,data_rocks$tps)))  + scale_x_discrete(breaks = c(600)) + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60)))


```

## Throughput per threads and workload, details. 
## Throughput per threads and workload, PerconaFT

```{r ft,  fig.width=36, fig.height=16, warning=FALSE, echo=FALSE}

for (t in nothreads) {
    subdata <- subset(data_ft, threads == t)
	gtitle <- paste("Percona Server for MongoDB / throughput (PerconaFT/", t," threads)")
	print(ggplot(subdata, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter(size=4) + scale_colour_discrete(name = "") + facet_grid(. ~ distribution) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle(gtitle) + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,subdata$tps)))  + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60)))
}
```

## Throughput per threads and workload, WiredTiger

```{r wt,  fig.width=36, fig.height=16, warning=FALSE, echo=FALSE}


for (t in nothreads) {
    subdata <- subset(data_wt, threads == t)
	gtitle <- paste("Percona Server for MongoDB / throughput (WiredTiger/", t," threads)")
	print(ggplot(subdata, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter(size=4) + scale_colour_discrete(name = "") + facet_grid(. ~ distribution) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle(gtitle) + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,subdata$tps)))  + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60)))
}
```

## Throughput per threads and workload, RocksDB

```{r rocks,  fig.width=36, fig.height=16, warning=FALSE, echo=FALSE}


for (t in nothreads) {
    subdata <- subset(data_rocks, threads == t)
	gtitle <- paste("Percona Server for MongoDB / throughput (RocksDB/", t," threads)")
	print(ggplot(subdata, aes(x=ts, y=tps, colour=as.factor(workload))) + geom_jitter(size=4) + scale_colour_discrete(name = "") + facet_grid(. ~ distribution) + xlab("Time in seconds (10 sec interval)") + ylab("Throughput (read/write ops per second)") + ggtitle(gtitle) + scale_y_continuous(breaks = extended_range_breaks()(rbind(0,subdata$tps)))  + expand_limits(x=0, y=0) + theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60)))
}
```
