---

title: "Percona Server for MongoDB 3.2.7: WiredTiger vs InMemory sysbench oltp performance"

author: "Percona Lab"
generated on:`r format(Sys.Date(), "%B %d, %Y")`
output:
  md_document:
    variant: markdown_github

---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(knitr)
library(plyr)

label_custom <- function(variable, value) {
    if (variable=="engine") {
       return (ifelse(value=="inmemory","inMemory","wiredTiger"))
    } else {
      return (as.character(value))
    }
}

shortBenchmarks <- read.csv("../data-short-benchmarks.csv", header=T)
longBenchmarks <- read.csv("../data-long-benchmarks.csv", header=T)

nothreads <- c(512,128,48,32)

```

# Percona Server for MongoDB 3.2.7-1.1 - WiredTiger vs InMemory sysbench oltp performance

## Setup

* WiredTiger: psmdb 3.2.7-1.1 
* InMemory: built from source, v3.2 percona-server-mongodb branch
* sysbench with mongodb support, oltp and oltp_ro scripts
* inMemorySizeGB / wiredTigerCacheSizeGB set to 32GB
* Data set: 8 collections, 6M documents per collection (12GB compressed)

## Benchmark procedure

* For WiredTiger: restore the datadir from binary backup before each experiment
* For InMemory: restore the datadir with mongorestore (taken with mongodump from the same data set used to create the binary backup for WiredTiger) before each experiment
* Sysbench runs of 60 seconds


```{r short, fig.width=36, fig.height=16, warning=FALSE, echo=FALSE}

for (d in c("uniform","pareto")) {
    for (wl in c("oltp", "insert")) {

    subdata <- subset(shortBenchmarks, distribution == d & workload == wl)

    p <- ggplot(subdata, aes(x=ts, y=tps, color=as.factor(engine))) +
        facet_grid(. ~ user_provided_threads, labeller = label_custom) +
        geom_jitter(size=8,width=0.2,height=0.2) +
        theme_bw () + theme(text = element_text(size=60)) + 
        labs(x="time (secs)", y="throughput (tps)", title=paste("WiredTiger vs InMemory throughput - ",d," - ",wl)) +
        scale_y_continuous(breaks=extended_range_breaks()(rbind(0,subdata$tps))) +
        theme(panel.grid = element_line(colour="#010101",size=1),
        panel.background = element_rect(colour="#000000"),
        plot.background = element_rect(colour="#000000"),
        strip.background = element_rect(colour="#010101"))
        print(p) 

    }
}

```


