---

title: "Percona Xtrabackup: Compression and Encryption performance"
author: "Percona Lab"
generated on:`r format(Sys.Date(), "%B %d, %Y")`
output:
  md_document:
    variant: markdown_github

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(knitr)
library(plyr)

label_custom <- function(variable, value) {
    if (value=="compression") {
        return("C")
    } else if (value=="encryption") {
        return("E")
    } else {
        return(as.character(value))
    }
}

data <- read.csv("../alldata.csv", header=T)
durations <- read.csv("../durations.csv", header=T)
diskstats <- read.csv("../diskstats.csv", header=T)

nothreads <- c(1,4,8,16,32)

disks <- c("hdd","ssd")

types <- c("encryption","compression")

```
# Percona Xtrabackup 2.3.4 - Encryption and Compression performance 

## Setup

* Client and server on the same machine 
* Sysbench oltp workload running during all tests
* 21GB datadir (restored between tests)
* CPU: 48 logical CPU threads (Intel(R) Xeon(R) CPU E5-2680 v3 @ 2.50GHz). 
* Memory: 120GB. 
* Disk: hdd (HGST HUH728080ALE600), ssd (Intel 3600 nvme) 
* Encryption (E) and Compression (C) tested with 1, 4, 8, 16 and 32 threads


## Backup duration 

Backup duration by type, number of threads, and disk type. The
horizontal line on each graph shows the duration for the baseline (non
compressed, non encrypted) backup. 

```{r global, fig.width=36, fig.height=16, warning=FALSE, echo=FALSE}



baseline_hdd <- as.numeric(subset(durations, type=="baseline" & disk == "hdd")$backup_duration)
baseline_ssd <- as.numeric(subset(durations, type=="baseline" & disk == "ssd")$backup_duration)
hdd <- subset(durations,disk == "hdd" & type != "baseline")
ssd <- subset(durations,disk == "ssd" & type != "baseline")
attach(hdd)
ggplot(hdd, aes(x=as.factor(threads),y=as.numeric(backup_duration),color=as.factor(type))) + 
scale_colour_discrete(name = "type") +
geom_hline(aes(yintercept=baseline_hdd)) + 
geom_point(size=8) + 
theme_bw() + 
labs(x="threads",y="duration (secs)",title="Backup duration - hdd") + expand_limits(x=0, y=0) + 
scale_y_continuous(breaks=extended_range_breaks()(rbind(0,backup_duration))) + 
theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60))
detach(hdd)
attach(ssd)
ggplot(ssd, aes(x=as.factor(threads),y=as.numeric(backup_duration),color=as.factor(type))) + 
scale_colour_discrete(name = "type") +
geom_hline(aes(yintercept=baseline_ssd)) + 
geom_point(size=8) + 
theme_bw() + 
labs(x="threads",y="duration (secs)",title="Backup duration - ssd") + expand_limits(x=0,y=0) +
scale_y_continuous(breaks=extended_range_breaks()(rbind(0,backup_duration))) + 
theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60))
detach(ssd)

#

```

## Impact on throughput

The following graphs show tps for sysbench oltp (16 threads, 10M rows
per table, 16 tables) while xtrabackup runs. Duration is not the same
for all graphs as backups don't all last the same (which is why we
can't facet on type/threads).

In all cases, the experiment was run as follows :
- sysbench oltp runs for 10 seconds
- xtrabackup starts
- sysbench oltp continues for 20 seconds after xtrabackup completes

```{r tps, fig.width=36, fig.height=16, warning=F, echo=F}
for (y in types) {
    for (d in disks) { 
        for (t in nothreads) {
            subdata <- subset(data, disk == d & type == y & user_provided_threads == t)
            attach(subdata)
            # print(paste(d, " ", y, " ", t))
            # print(head(subdata))
            p = ggplot(subdata, aes(x=ts, y=tps)) +
            geom_jitter(size=8) +
            theme_bw() +
            labs(x="time in secs (10 sec incr)", y="throughput (tps)", title=paste("OLTP throughput during backup - ",d," - ",y," - ",t," threads")) + expand_limits(x=0,y=0) +
            scale_y_continuous(breaks=extended_range_breaks()(rbind(0,tps))) +
            theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60))
            print(p)
            detach(subdata)
        }
    }
}

# hdd <- subset(data, disk == "hdd" & type != "baseline")
# ssd <- subset(data, disk == "ssd" & type != "baseline")
# attach(hdd)
# ggplot(hdd, aes(x=ts, y=tps, color=as.factor(type))) + facet_grid(. ~ user_provided_threads) +
# scale_colour_discrete(name = "type") +
# geom_jitter(size=8) +
# theme_bw() +
# labs(x="time in secs (10 sec incr)", y="throughput (tps)", title="OLTP throughput during backup - hdd") + expand_limits(x=0,y=0) +
# scale_y_continuous(breaks=extended_range_breaks()(rbind(0,tps))) +
# theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60))
#         
# detach(hdd)
# attach(ssd)
# ggplot(ssd, aes(x=ts, y=tps, color=as.factor(type))) + facet_grid(. ~ user_provided_threads) +
# scale_colour_discrete(name = "type") +
# geom_jitter(size=8) +
# theme_bw() +
# labs(x="time in secs (10 sec incr)", y="throughput (tps)", title="OLTP throughput during backup - ssd") + expand_limits(x=0,y=0) +
# scale_y_continuous(breaks=extended_range_breaks()(rbind(0,tps))) +
# theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60))
# detach(ssd)

```


