---

title: "Percona Server for MongoDB: Range Queries performance on RocksDB and WiredTiger"
author: "Percona Lab"
generated on:`r format(Sys.Date(), "%B %d, %Y")`
output:
  md_document:
    variant: markdown_github

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(knitr)
library(plyr)

label_custom <- function(variable, value) {
    if (variable=="version") {
       return(sub("upstream","M",sub("psmdb","P",value)))
    } else if (variable=="range_size" | variable=="Group.4") {
		return(paste("rs: ",value/1000,"k"))
    }else {
      return (as.character(value))
    }
}

data <- read.csv("../../alldata.csv", header=T)

data_uniform <- subset(data, distribution == "uniform")
data_pareto <- subset(data, distribution == "pareto") 

data_wt <- subset(data, engine == "wt") 
data_rocks <- subset(data, engine == "rocks") 


nothreads <- c(1,4,16,32,48,128,512)
disks <- c("hdd","slowssd","fastssd")
#ranges <- c(1000,10000,100000)
ranges <- c(1000,10000)

```
# Percona Server for MongoDB 3.2.0-1.0 - Range queries performance 

## Setup

* Client and server on the same machine 
* Client sofwware is sysbench (https://github.com/Percona-Lab/sysbench/tree/dev-mongodb-support).
* CPU: 48 logical CPU threads (Intel(R) Xeon(R) CPU E5-2680 v3 @ 2.50GHz). 
* Memory: 120GB or 20GB (the latter limited via cgroup).
* Disk: hdd (HGST HUH728080ALE600), slowssd (Crucial CT960M500SSD1), fastssd (Intel 3600 nvme) 
* sysbench with mongodb support, 16 collections x 10M or 60M documents (~35GB or ~200G uncompressed), uniform and pareto distributions. 
* Workloads are labeled as:
- cpubound (10M documents per collection, fastssd storage)
- iobound (60M documents per collection, fastssd and slowssd storage, 120GB RAM)
- iobound_heavy (same as previous, but with 20GB RAM)

## Throughput per threads and workload for range size 1k documents

```{r global, fig.width=36, fig.height=16, warning=FALSE, echo=FALSE}

# > head(aggdata_pareto)
#   Group.1 Group.2 Group.3 Group.4 Group.5         x
# 1   rocks       1 iobound    10000 fastssd  3135.991

for (d in disks) {
    subdata <- subset(data_pareto, disk == d & range_size == 1000)
    aggdata_pareto <- aggregate(subdata$tps, by=list(subdata$engine, subdata$user_provided_threads, subdata$workload), FUN=function(x) quantile(x, probs=0.99))
    attach(aggdata_pareto)
    gtitle <- paste("sysbench Ranges - Pareto (",d,")")
    print(ggplot(aggdata_pareto, aes(x=as.factor(Group.2),y=as.numeric(x),color=as.factor(Group.1),group=Group.1)) + facet_grid(. ~ Group.3, labeller=label_custom) +geom_line()+geom_point(size=4) + labs(x="Threads",y="Throughput,tps",title=gtitle)+scale_color_tableau(name="Engine")+scale_y_continuous(breaks=extended_range_breaks()(rbind(0,x)),labels = scales::comma)+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60)))

  
    detach(aggdata_pareto)
    subdata <- subset(data_uniform, disk == d & range_size == 1000)
    aggdata_uniform <- aggregate(subdata$tps, by=list(subdata$engine, subdata$user_provided_threads, subdata$workload), FUN=function(x) quantile(x, probs=0.99))
    attach(aggdata_uniform)
    gtitle <- paste("sysbench Ranges - Uniform (",d,")")
    print(ggplot(aggdata_uniform, aes(x=as.factor(Group.2),y=as.numeric(x),color=as.factor(Group.1),group=Group.1))+geom_line()+geom_point(size=4) + facet_grid(. ~ Group.3, labeller=label_custom) +labs(x="Threads",y="Throughput,tps",title=gtitle)+scale_color_tableau(name="Engine")+scale_y_continuous(breaks=extended_range_breaks()(rbind(0,x)),labels = scales::comma)+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+theme_bw() + theme(panel.grid = element_line(colour="#010101",size=1), panel.background = element_rect(colour="#000000"), plot.background = element_rect(colour="#000000"), strip.background = element_rect(colour="#010101"), text=element_text(size=50), strip.text=element_text(size=60)))
    detach(aggdata_uniform)

}


```

