---
title: "local PK"
author: "None"
date: "March 17, 2016"
--output: html_document
output:
  md_document:
    variant: markdown_github

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(knitr)

tm<-theme(legend.position="bottom",
          text=element_text(family="Georgia"),
          strip.background = element_rect(colour="red", fill="#CCCCFF"))

guides(colour = guide_legend(override.aes = list(size=4)))

data = read.table("../summary.csv",sep=",",header=F)
data1=subset(data,V1>100)
attach(data1)
aggdata <-aggregate(data1, by=list(V4,V5),FUN=mean, na.rm=TRUE)
```
# Percona Server 5.7 - monitoring overhead

## Setup

* Client (sysbench) and server are on the same server 
* CPU: 56 logical CPU threads servers Intel(R) Xeon(R) CPU E5-2683 v3 @ 2.00GHz
* sysbench 100 tables x 1mln rows, uniform distribution
* OS: Ubuntu 15.10 (Wily Werewolf)
* Kernel 4.2.0-30-generic

```{r test, eval=FALSE, fig.height=8, fig.width=10, warning=FALSE, include=FALSE}
ss=subset(aggdata)

m <- ggplot(ss, aes(x=as.factor(Group.2),y=as.numeric(V2),color=as.factor(Group.1),group=Group.1))
m+geom_line()+geom_point(size=1)+labs(x="Threads",y="Throughput,tps",title="sysbench read-only")+scale_color_tableau(name="Version")+scale_y_continuous(breaks=seq(0, 480000, 20000),labels = scales::comma)+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+tm
```
```{r test2, eval=FALSE, fig.height=8, fig.width=10, warning=FALSE, include=FALSE}
ss=subset(aggdata)

m <- ggplot(ss, aes(x=as.factor(Group.2),y=as.numeric(V3),color=as.factor(Group.1),group=Group.1))
m+geom_line()+geom_point(size=1)+labs(x="Threads",y="Throughput,tps",title="sysbench read-only")+scale_color_tableau(name="Version")+scale_y_log10(breaks=c(.001,.01,0.05,.1,.5,1,10,100,250,500,1000),limits = c(.01,1000))
#+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+tm
```

## Results with plugins

* PS 5.7
* query_rt_plugin : `query_response_time` plugins installed (but `query_response_time_stats = off`)
* qrt_enabled:  `query_response_time` plugins installed and `query_response_time_stats = on`
* audit.no_policy: audit plugin installed, but `audit_log_policy=NONE`

```{r plugins, echo=FALSE, warning=FALSE,fig.width=10, fig.height=8}
ss=subset(aggdata,(Group.2<=1000) & (Group.1 %in% c("ps57.long.try3","ps57.audit.no_policy","ps57.qrt_enabled","ps57.long.query_rt_plugin")))
#ss=subset(aggdata)

m <- ggplot(ss, 
            aes(x=as.factor(Group.2),y=as.numeric(V2),color=as.factor(Group.1),group=Group.1))
m+geom_line()+geom_point(size=1)+labs(x="Threads",y="Throughput,OPS",title="sysbench PK lookup")+scale_color_tableau(name="Version")+scale_y_continuous(breaks=seq(0, 450000, 20000),labels = scales::comma)+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+tm
```

## Results with userstat

* PS 5.7
* userstat - userstat enabled (`userstat=1`)

```{r userstat, echo=FALSE, warning=FALSE,fig.width=10, fig.height=8}
ss=subset(aggdata,(Group.2<=1000) & (Group.1 %in% c("ps57.long.try3","ps57.userstat")))
#ss=subset(aggdata)

m <- ggplot(ss, 
            aes(x=as.factor(Group.2),y=as.numeric(V2),color=as.factor(Group.1),group=Group.1))
m+geom_line()+geom_point(size=1)+labs(x="Threads",y="Throughput,OPS",title="sysbench PK lookup")+scale_color_tableau(name="Version")+scale_y_continuous(breaks=seq(0, 450000, 20000),labels = scales::comma)+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+tm
```

## Results with slowlog

* PS 5.7
* slowlog - slowlog enabled 
    * slow-query-log=ON
    * slow-query-log-file=slow.log
    * long_query_time=0
    * loose_slow_query_log_use_global_control=all
    * loose_log_slow_verbosity=full 
    * loose_log_slow_rate_type=query
    * loose_log_slow_rate_limit=5000
    * loose_slow_query_log_use_global_control=all
    * loose_slow_query_log_always_write_time=1  


```{r slowlog, echo=FALSE, warning=FALSE,fig.width=10, fig.height=8}
ss=subset(aggdata,(Group.2<=1000) & (Group.1 %in% c("ps57.long.try3","ps57.slowlog")))
#ss=subset(aggdata)

m <- ggplot(ss, 
            aes(x=as.factor(Group.2),y=as.numeric(V2),color=as.factor(Group.1),group=Group.1))
m+geom_line()+geom_point(size=1)+labs(x="Threads",y="Throughput,OPS",title="sysbench PK lookup")+scale_color_tableau(name="Version")+scale_y_continuous(breaks=seq(0, 450000, 20000),labels = scales::comma)+theme(axis.text.x  = element_text(angle=45, vjust=0.5))+tm
```
