---

title: "Percona Xtrabackup: Compression and Encryption performance"
author: "Percona Lab"
generated on:`r format(Sys.Date(), "%B %d, %Y")`
output:
  html_document:
    self_contained: false 
    lib_dir: libs
<!--  md_document:
    variant: markdown_github -->

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(knitr)
library(plyr)
library(gridExtra)

label_custom <- function(variable, value) {
    if (value=="compression") {
        return("C")
    } else if (value=="encryption") {
        return("E")
    } else {
        return(as.character(value))
    }
}

data <- read.csv("../../alldata.csv", header=T)
dataParallel <- read.csv("../../alldata-parallel.csv", header=T)
durations <- read.csv("../../durations.csv", header=T)
durationsParallel <- read.csv("../../durations-parallel.csv", header=T)
diskstats <- read.csv("../../diskstats.csv", header=T)
diskstatsParallel <- read.csv("../../diskstats-parallel.csv", header=T)
vmstatParallel <- read.csv("../../vmstat-parallel.csv", header=T)

nothreads <- c(1,4,8,16,32,48,62)
noparthreads <- c(1,4,8,16,32)

disks <- c("hdd","ssd")

types <- c("encryption","compression", "xbstream_compressed", "xbstream_qpress")

```
# Percona Xtrabackup 2.3.4 - Encryption and Compression performance 

## Setup

* Client and server on the same machine 
* Sysbench oltp workload running during all tests
* 21GB datadir (restored between tests)
* CPU: 48 logical CPU threads (Intel(R) Xeon(R) CPU E5-2680 v3 @ 2.50GHz). 
* Memory: 120GB. 
* Disk: hdd (HGST HUH728080ALE600), ssd (Intel 3600 nvme) 
* Encryption (E) and Compression (C) tested with 1, 4, 8, 16 and 32 threads


## Backup duration 

Backup duration by type, number of threads, and disk type, faceted by
--parallel threads. The
horizontal line on each graph shows the duration for the baseline (non
compressed, non encrypted) backup. 

```{r global, fig.width=36, fig.height=16, warning=FALSE, echo=FALSE}

baseline_ssd <- as.numeric(subset(durationsParallel, type=="baseline" & disk == "ssd")$backup_duration)
ssd <- subset(durationsParallel,disk == "ssd" & type != "baseline")
attach(ssd)
ggplot(ssd, aes(x=as.factor(threads),y=as.numeric(backup_duration),color=as.factor(type),label=backup_duration)) + 
scale_colour_discrete(name = "type") +
geom_hline(aes(yintercept=baseline_ssd)) + 
#geom_jitter(size=8,width=0.2,height=0.2) + 
geom_text(size=18) +
facet_grid(parallel_threads ~ .) +
theme_bw() + 
labs(x="threads",y="duration (secs)",title="Backup duration - ssd") + expand_limits(x=0,y=0) +
scale_y_continuous(breaks=extended_range_breaks()(rbind(0,backup_duration))) + 
theme(panel.grid = element_line(colour="#010101",size=1),
      panel.background = element_rect(colour="#000000"),
      plot.background = element_rect(colour="#000000"),
      strip.background = element_rect(colour="#010101"),
      text=element_text(size=50),
      strip.text=element_text(size=60))

print(ssd[order(ssd$backup_duration),])

#

```

